---
title: "Text etc analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(sf)
library(ggplot2)
library(tidytext)
library(plotly)
library(scales)
library(crosstalk)
```

```{r}
StHimark <- st_read(
  "DC5-Data/Sensor Data and Maps/StHimarkNeighborhoodShapefiles/StHimark.shp")
```

# Text Analysis

```{r}
#Reading in the data
YInt_data <- read_csv("DC5-Data/Y*Int Social Media Data/YInt.csv")
```

```{r}
#Tidying the data

data(stop_words)
#Goal: I would like to be able to use token = "tweets" in order to preserve # and @ (which are important in understanding tweeting patterns). I don't understand the error message that comes up when I do that, though
YInt_word <- YInt_data %>%
  unnest_tokens(word, message) %>% 
  anti_join(stop_words)

YInt_word %>% 
  count(word, sort = TRUE)
```



# Trying to overlay word clouds on map

```{r}
map <- ggplot() + 
  geom_sf(data = StHimark, size = 0.25) + 
  geom_sf_label(data = StHimark, aes(label = Nbrhood)) +
  #ggtitle("Boundary Plot") + 
  coord_sf() +
  theme_void() +
  theme(legend.position = "none")
plotly_map <- ggplotly(map)
```



```{r}
text_points <- sf::st_point_on_surface(StHimark)


# retrieve the coordinates
text_coords <- as.data.frame(sf::st_coordinates(text_points))
text_coords$NAME <- StHimark$Nbrhood
neighborhoods_list <- c()
for (i in text_coords$NAME) {
  append(neighborhoods_list, i)
  neighborhoods_list <- c(neighborhoods_list, i)
}
names <- neighborhoods_list
```


# Word frequencies
From www.tidytextmining.com/tidytext.html

```{r}
word_frequency <- YInt_word

# removing na values -- from https://stackoverflow.com/questions/35912616/remove-n-a-from-the-data-frame
word_frequency <- na.omit(word_frequency)

# getting rid of locations that aren't neighborhoods in the map (it'd be great to look at those but not what I'm doing right now)
word_frequency_locations <- word_frequency %>% 
  filter(location %in% names)
```


```{r}

# Let's see if we can get a word frequency comparison graph for one neighborhood versus the others -- let's say, Broadview
word_frequency_locations %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>% 
  count(location, word) %>% 
  group_by(location) %>% 
  mutate(proportion = n / sum(n)) %>% 
  select(-n)%>% 
  pivot_wider(names_from = location, 
              values_from = proportion) %>% 
  na.omit() %>% 
  pivot_longer(-c("Broadview", "word"), names_to = "location", values_to = "proportion") %>% 
  group_by(word) %>% 
  mutate(other_proportion = mean(proportion)) %>% 
  ggplot(aes(x = proportion, y = Broadview, 
                      color = abs(Broadview - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslategray4", high = "gray75") +
  #facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Broadview", x = NULL)
```

```{r}
word_frequency_locations %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%  
  group_by(location) %>% 
  mutate(count = n(),
         proportion = count / sum(count)) %>% 
  select(-count)%>% 
  pivot_wider(names_from = location, 
              values_from = proportion) %>% 
  na.omit() %>% 
  pivot_longer(-c("time", "account", "Broadview", "word"), names_to = "location", values_to = "proportion") %>% 
  group_by(word) %>% 
  mutate(other_proportion = mean(proportion)) %>% 
  ggplot(aes(x = proportion, y = Broadview, 
                      color = abs(Broadview - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslategray4", high = "gray75") +
  #facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Broadview", x = NULL)
```

```{r}

# Let's see if we can get a word frequency comparison graph for one neighborhood versus the others -- let's say, Broadview
word_frequency_locations %>% 
  mutate(word = str_extract(word, "[a-z']+"),
         tot_num_words = n()) %>% 
  #count(location, word) %>% 
  group_by(location) %>% 
  mutate(words_in_location = n()) %>% 
  group_by(location, word) %>% 
  mutate(loc_word_count = n(),
         loc_proportion = loc_word_count / words_in_location) %>% 
  group_by(word) %>% 
  mutate(all_word_count = n(),
         all_proportion = all_word_count / tot_num_words,
         other_word_count = all_word_count - loc_word_count,
         words_in_other_location = tot_num_words - words_in_location,
         other_proportion = other_word_count / words_in_other_location) %>% 
  distinct(location, loc_proportion, .keep_all = TRUE) %>% 
  select(location, word, loc_proportion, other_proportion) %>% 
  filter(location == "Broadview") %>% 
  mutate(loc_proportion = ifelse(is.na(loc_proportion), 0, loc_proportion)) %>% 
  na.omit() %>% 
  ggplot(aes(x = other_proportion, y = loc_proportion, 
                      color = abs(loc_proportion - other_proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "gray75", high = "darkslategray4") +
  #facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "Broadview", x = "Other Neighborhoods")
```
```{r}
StHimark_word <- StHimark %>% 
  mutate(location = Nbrhood) %>% 
  select(geometry, location)
```

```{r}
# Let's see if we can get a word frequency comparison graph for one neighborhood versus the others -- let's say, Broadview
all_data <- word_frequency_locations %>% 
  mutate(word = str_extract(word, "[a-z']+"),
         tot_num_words = n()) %>% 
  #count(location, word) %>% 
  group_by(location) %>% 
  mutate(words_in_location = n()) %>% 
  group_by(location, word) %>% 
  mutate(loc_word_count = n(),
         loc_proportion = loc_word_count / words_in_location) %>% 
  group_by(word) %>% 
  mutate(all_word_count = n(),
         all_proportion = all_word_count / tot_num_words,
         other_word_count = all_word_count - loc_word_count,
         words_in_other_location = tot_num_words - words_in_location,
         other_proportion = other_word_count / words_in_other_location) %>% 
  distinct(location, loc_proportion, .keep_all = TRUE) %>% 
  select(time, location, word, loc_proportion, other_proportion, all_proportion) %>% 
  #filter(location == "Broadview") %>% 
  mutate(loc_proportion = ifelse(is.na(loc_proportion), 0, loc_proportion)) %>% 
  na.omit() %>% 
  left_join(StHimark_word, by = "location")

```

```{r}
new_data <- SharedData$new(all_data)
```

```{r}
Broadview <- all_data %>% 
  select(-geometry) %>% 
  #filter(location == "Broadview") %>% 
  ggplot(aes(x = all_proportion, y = loc_proportion, 
                      color = abs(loc_proportion - all_proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "gray75", high = "darkslategray4") +
  #facet_wrap(~author, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "", x = "Other Neighborhoods") +
  facet_wrap(~location)
```

```{r}
Broadview %>% theme_minimal()
  
```

```{r}
#neighborhood = "Broadview"
fig <- all_data %>%
  select(-geometry) %>%
  mutate(diff = abs(loc_proportion - other_proportion),
         hour = substr(as.character(time), 12, 13)) %>%
  #filter(location == "Broadview") %>% 
  plot_ly(
    x = ~other_proportion, 
    y = ~loc_proportion, 
    frame = ~as.character(hour), 
    size = ~diff, sizes = c(10, 50),
    color = ~location,
    text = ~word,
    hoverinfo = "text") %>% 
  layout(xaxis = list(
    title = "Word Frequency in All Neighborhoods"
  ),
  yaxis = list(
    title = "Word Frequency in Neighborhood"
  )) %>%
  animation_slider(
    currentvalue = list(prefix = "HOUR ")
  )
```
```{r}
library(htmlwidgets)

saveWidget(as_widget(fig), "output-graphs/plotly_word.html")
```
, 
    marker = list(
      sizemode = 'diameter',
      colorscale = list(c(0, 'rgba(255, 199, 130,0.75)'),
                        c(1, 'rgba(173, 30, 2, 1)'))))




```{r}
bscols(widths = c(3,NA,NA),
       list(
         filter_checkbox("location", "Neighborhood", new_data, ~location, inline = TRUE)
       ),
       ggplotly(Broadview))
```


```{r}
d <- SharedData$new(mtcars)
# make a scatterplot of disp vs mpg
scatterplot <- plot_ly(d, x = ~mpg, y = ~disp) %>%
  add_markers(color = I("navy"))
# define two subplots: boxplot and scatterplot
subplot(
  # boxplot of disp
  plot_ly(d, y = ~disp) %>% 
    add_boxplot(name = "overall", 
                color = I("navy")),
  # scatterplot of disp vs mpg
  scatterplot, 
  shareY = TRUE, titleX = T) %>% 
  layout(dragmode = "select")
```

```{r}
new_map <- new_data %>% 
  select(location, geometry) %>% 
  ggplot() +
  geom_sf(data = StHimark, size = 0.25) + 
  geom_sf_text(data = StHimark, aes(label = Nbrhood))
new_plotly_map <- ggplotly(new_map)
```


```{r}
subplot(new_plotly_map,
        ggplotly(Broadview))
```

```{r}
MobileSensorReadings <- read_csv("DC5-Data/Sensor Data and Maps/MobileSensorReadings.csv") %>% 
  mutate(time = as.POSIXct(Timestamp)) %>% select(-Timestamp)

set.seed(21)
small_MobileSensorReadings <- MobileSensorReadings %>%
  sample_frac(0.2)

set.seed(21)
MobileSensorReadings_byloc <- small_MobileSensorReadings %>%
  sample_frac(0.01) %>% # test smaller
  mutate(hour=lubridate::floor_date(time, "1 hour")) %>%
  group_by(Long, Lat, hour) %>% mutate(hourly_Value = sum(Value))
```

```{r}
fig <- MobileSensorReadings_byloc %>%
  plot_ly(
    x = ~Long, y = ~Lat, frame = ~as.character(hour), 
    size = ~hourly_Value, sizes = c(10, 50),
    color = ~hourly_Value, 
    type = 'scatter', mode = 'markers', 
    marker = list(
      sizemode = 'diameter',
      colorscale = list(c(0, 'rgba(255, 199, 130,0.75)'),
                        c(1, 'rgba(173, 30, 2, 1)'))))
fig
```
      , showscale=T,
      cauto = F, cmin = 0, cmax =  max(MobileSensorReadings_byloc$hourly_Value),
        # 5172437 for the entire dataset
      line = list(color = 'rgba(51, 6, 0, 1)', width = 2)
      )
    )%>%
    animation_opts(0) %>%
  layout(
    images = list(
      source = raster2uri(as.raster(img1)),
      x = -119.9999, y = 0.008,
      sizex = 0.288152, sizey = 0.230372,
      xref = "x", yref = "y",
      xanchor = "left", yanchor = "bottom",
      sizing = "stretch", opacity = 0.7,
      layer = "below"
    ), xaxis = list(title=""), yaxis = list(title="")
  ) %>%
  animation_slider(
    currentvalue = list(prefix = "timestamp ", font = list(color="red"))
  ) %>% hide_colorbar()
```


