---
title: "Main Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidyr)
library(readr)
library(sf)
library(ggplot2)
library(rgdal)
library(broom)
library(tidytext)
library(ggwordcloud)
library(plotly)
```


# Sensor Data

## Import
```{r}
# Solved the datetime problem, just change class using other functions, not readr

MobileSensorReadings <- read_csv("DC5-Data/Sensor Data and Maps/MobileSensorReadings.csv") %>% 
  mutate(time = as.POSIXct(Timestamp)) %>% select(-Timestamp)

StaticSensorLocations <- read_csv("DC5-Data/Sensor Data and Maps/StaticSensorLocations.csv")

StaticSensorReadings <- read_csv("DC5-Data/Sensor Data and Maps/StaticSensorReadings.csv") %>% 
  mutate(time = as.POSIXct(Timestamp)) %>% select(-Timestamp)
```

```{r}
StHimark <- st_read(
  "DC5-Data/Sensor Data and Maps/StHimarkNeighborhoodShapefiles/StHimark.shp")
```

## Shapefile 

```{r}
map <- ggplot() + 
  geom_sf(data = StHimark, size = 0.25, color = "white", fill = "#69b3a2") + 
  ggtitle("Boundary Plot") + 
  coord_sf() +
  theme_void() 
# +
#   geom_point(data = StaticSensorLocations, aes(x = Long, y = Lat))
```

this one has neighbourhoods

```{r}
my_spdf <- readOGR(
  dsn= "DC5-Data/Sensor Data and Maps/StHimarkNeighborhoodShapefiles/",
  layer="StHimark",
  verbose=FALSE)

spdf_fortified <- tidy(my_spdf)
# Plot it
map2 <- ggplot() +
  geom_polygon(data = spdf_fortified, aes( x = long, y = lat, group = group),
               fill="#69b3a2", color="white") +
  theme_void()
```

ask about extensions and shapefile, whether we can just use the shapefile itself 


## Sensor 

### Mobile

```{r}
MobileSensorReadings_by_min <- MobileSensorReadings %>%
  group_by(time) %>% mutate(min_Value = sum(Value)) %>% distinct(time, .keep_all=T)%>%
  select(time, min_Value)
max(MobileSensorReadings_by_min$min_Value) # 2020-04-09 02:43:25	
ggplot(MobileSensorReadings_by_min, aes(x=time, y=min_Value)) + geom_line()
```

By location

```{r}
# map + geom_point(data = MobileSensorReadings, aes(x=Long, y=Lat))
ggplot() + geom_point(data = MobileSensorReadings[1:2000,], aes(x=Long, y=Lat))
MobileSensorReadings_byloc <- MobileSensorReadings%>%
  group_by(Long, Lat, time) %>% mutate(min_Value = sum(Value))

fig <- MobileSensorReadings_byloc %>%
  plot_ly(x = ~Long, y = ~Lat, frame = ~time, size = ~Value, type = 'scatter', mode = 'markers', showlegend = T) #%>%
  # layout(xaxis = list(type = "log"))
fig
```



### Static

```{r}

```

# Text Analysis

```{r}
#Reading in the data
YInt_data <- read_csv("DC5-Data/Y*Int Social Media Data/YInt.csv")
```

```{r}
#Tidying the data

data(stop_words)
#Goal: I would like to be able to use token = "tweets" in order to preserve # and @ (which are important in understanding tweeting patterns). I don't understand the error message that comes up when I do that, though
YInt_word <- YInt_data %>%
  unnest_tokens(word, message) %>% 
  anti_join(stop_words)

YInt_word %>% 
  count(word, sort = TRUE)
```

```{r}
#There was something about a missing dog?
YInt_word %>% filter(str_detect(word, "missing"))
```

```{r}
#Generating a word cloud from the most frequent words

wordclouddata<- YInt_word %>% 
  #group_by(location) %>% 
  count(word, sort = TRUE) %>% 
  head(100)
#glimpse(wordclouddata)

set.seed(53)
ggplot(wordclouddata, aes(label = word, size = n)) +
  geom_text_wordcloud() #+
  #scale_size_area(max_size = 10) +
  #theme_minimal()
```


Goals from group meeting:
- word cloud for each location (preferably overlaid on map)
- missing dog (dachschund)
- anything interesting in messages


# Trying to overlay word clouds on map

```{r}
map2 <- ggplot() + 
  geom_sf(data = StHimark, size = 0.25, aes(fill = Nbrhood, color = Nbrhood)) + 
  ggtitle("Boundary Plot") + 
  coord_sf() +
  theme_void() +
  theme(legend.position = "none")
```

```{r}
#https://www.tutorialkart.com/r-tutorial/concatenate-two-or-more-strings-in-r/
a <- "a"
b <- paste(a,"b", sep="")
```

```{r}
#https://plotly.com/r/subplots/
wordclouddata<- YInt_word %>% 
  filter(location == "Old Town") %>% 
  count(word, sort = TRUE) %>% 
  head(10)

set.seed(53)
wordcloud <- ggplot(wordclouddata, aes(label = word, size = n)) +
  geom_text_wordcloud() #+
  #scale_size_area(max_size = 10) +
  #theme_minimal()

#subplot(map2, wordcloud)
#THIS WON'T WORK BECAUSE WORDCLOUDS HAVEN'T BEEN COMBINED WITH PLOTLY YET i'm so sad :'(
```
```{r}
x <- 1:3 
y <- 1:3
logos <- c("r-logo", "penguin", "rstudio")
# base64 encoded string of each image
uris <- purrr::map_chr(
  logos, ~ base64enc::dataURI(file = sprintf("images/%s.png", .x))
)
# hoverinfo = "none" will hide the plotly.js tooltip, but the 
# plotly_hover event will still fire
plot_ly(hoverinfo = "none") %>%
  add_text(x = x, y = y, customdata = uris, text = logos) %>%
  htmlwidgets::onRender(readLines("js/tooltip-image.js"))
```
Okay so THAT WORKED AND IT SHOWS IMAGES!!!
VERY IMPORTANT: source!!! I whole-scale copied and pasted that part, including the .js file which made the tooltip even possible, and I don't even know javascript so I should NOT take credit for that!! I got it from here: https://plotly-r.com/supplying-custom-data.html#fig:tooltip-image

Info on ggsave: https://www.tutorialgateway.org/save-r-ggplot-using-ggsave/
```{r}
location_word_cloud <- function(neighborhood) {
  
wordclouddata<- YInt_word %>% 
  filter(location == neighborhood) %>% 
  count(word, sort = TRUE) %>% 
  head(100)

set.seed(53)
wordcloud <- ggplot(wordclouddata, aes(label = word, size = n)) +
  geom_text_wordcloud() +
  #scale_size_area(max_size = 10) +
  theme_minimal()

name <- paste(neighborhood, ".png", sep = "")
ggsave(path = "images", filename = name)

}
#I wasn't sure if i could save within a function but apparently i can yay https://stackoverflow.com/questions/28176528/saving-within-a-function-in-r

```

```{r}
#checking --- IT WORKS!
location_word_cloud("East Parton")
```

```{r}
neighborhoods <- list(levels(StHimark$Nbrhood))
#problem: it was giving me the levels and not just the names https://stackoverflow.com/questions/27676404/list-all-factor-levels-of-a-data-frame
pmap(neighborhoods, location_word_cloud)
```


Okay so now I need to find a way to connect this to the map. For the custom js tooltip, I need to put text onto the map. I'm not sure if a normal geom_sf label will work, so I'm going to add text using geom_text onto a point in each neighborhood. However, in order to do this I need a point that is definitely within each neighborhood -- I'll try st_point_on_surface, found from https://r-spatial.github.io/sf/reference/geos_unary.html

Wait I found a resource that walks you through doing exactly that: https://yutani.rbind.io/post/geom-sf-text-and-geom-sf-label-are-coming/

```{r}
text_points <- sf::st_point_on_surface(StHimark)


# retrieve the coordinates
text_coords <- as.data.frame(sf::st_coordinates(text_points))
text_coords$NAME <- StHimark$Nbrhood
```

```{r}
map4 <- ggplot() +
  geom_sf(data = StHimark, aes(fill = Nbrhood)) +
  geom_text(data = text_coords, aes(X, Y, label = NAME), color = "white") +
  theme_void() +
  theme(legend.position = "none")
```

```{r}
uris <- purrr::map_chr(
  neighborhoods, ~ base64enc::dataURI(file = sprintf("images/%s.png", .x))
)
ggplotly(map4) %>%
  htmlwidgets::onRender(readLines("js/tooltip-image.js"))
```

```{r}
neighborhoods
logos <- c("r-logo", "penguin", "rstudio")
logos
```

Hmm I wonder if the problem is that the neighborhoods list doesn't look like the logos list -- maybe that's preventing it from being a description for the filename.
