---
title: "Sensor Data - Nage"
author: "Nage Ngo"
date: "4/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, error = F)
library(tidyverse)
library(sf)
library(ggplot2)
library(plotly)
```

Sensor Data

## Import
```{r csv and images}
# Solved the datetime problem, just change class using other functions, not readr

MobileSensorReadings <- read_csv("DC5-Data/Sensor Data and Maps/MobileSensorReadings.csv") %>% 
  mutate(time = as.POSIXct(Timestamp)) %>% select(-Timestamp)

StaticSensorLocations <- read_csv("DC5-Data/Sensor Data and Maps/StaticSensorLocations.csv")

StaticSensorReadings <- read_csv("DC5-Data/Sensor Data and Maps/StaticSensorReadings.csv") %>% 
  mutate(time = as.POSIXct(Timestamp)) %>% select(-Timestamp)

# Image no label with colored neighborhoods
img <- png::readPNG("DC5-Data/Sensor Data and Maps/StHimarkNeighborhoodMapNoLabels.png")
img1<- png::readPNG("DC5-Data/Sensor Data and Maps/StHimarkNeighborhoodMap.png")
```

```{r shapefile}
StHimark <- st_read(
  "DC5-Data/Sensor Data and Maps/StHimarkNeighborhoodShapefiles/StHimark.shp")
```

## Shapefile 

```{r}
map <- ggplot() + 
  geom_sf(data = StHimark, size = 0.25, color = "white", fill = "#69b3a2") + 
  ggtitle("Boundary Plot") + 
  # coord_sf(xlim = c(0,100), ylim = c(0,100)) +
  theme_void() 

# ggplotly(map)
```

ask about extensions and shapefile, whether we can just use the shapefile itself 


## Sensor 

### Mobile

Aggregate through time 

```{r time line plot}
MobileSensorReadings_by_min <- MobileSensorReadings %>%
  group_by(time) %>% mutate(min_Value = sum(Value)) %>% distinct(time, .keep_all=T)%>%
  select(time, min_Value)
max(MobileSensorReadings_by_min$min_Value) # 2020-04-09 02:43:25	
ggplot(MobileSensorReadings_by_min, aes(x=time, y=min_Value)) + geom_line()
```


```{r clean and sample}
set.seed(21)

MobileSensorReadings_t <- MobileSensorReadings %>%
  mutate(hour=lubridate::floor_date(time, "1 hour")) %>%
  group_by(Long, Lat, hour) %>% mutate(hourly_Value = sum(Value))
MobileSensorReadings_byloc <- MobileSensorReadings_t %>% 
    sample_frac(0.0022) # test smaller
```

By location

```{r map and mobile hourly}
fig <- MobileSensorReadings_byloc %>%
  plot_ly(
    x = ~Long, y = ~Lat, frame = ~as.character(hour), 
    size = ~hourly_Value, sizes = c(10, 50),
    color = ~hourly_Value, 
    type = 'scatter', mode = 'markers', 
    marker = list(
      sizemode = 'diameter',
      colorscale = list(c(0, 'rgba(255, 199, 130,0.75)'),
                        c(1, 'rgba(173, 30, 2, 1)')), showscale=T,
      cauto = F, cmin = 0, cmax =  max(MobileSensorReadings_byloc$hourly_Value),
        # 5172437 for the entire dataset
      line = list(color = 'rgba(51, 6, 0, 1)', width = 2)
      )
    )%>%
  animation_opts(0) %>%
  layout(
    images = list(
      source = raster2uri(as.raster(img1)),
      x = -119.9999, y = 0.008,
      sizex = 0.288152, sizey = 0.230372,
      xref = "x", yref = "y",
      xanchor = "left", yanchor = "bottom",
      sizing = "stretch", opacity = 0.7,
      layer = "below"
    ), xaxis = list(title=""), yaxis = list(title="")
  ) %>%
  animation_slider(
    currentvalue = list(prefix = "timestamp ", font = list(color="red"))
  ) %>% hide_colorbar()

fig
```


### Static

map 

```{r positions of static }
# change type of `Sensor-id`
StaticSensorLocations$`Sensor-id`<- as.character(StaticSensorLocations$`Sensor-id`)

ggplot(data = StaticSensorLocations, aes(x=Long, y=Lat)) + 
  scale_y_continuous(limits = c(min(MobileSensorReadings$Lat),
                                max(MobileSensorReadings$Lat)),
                     expand = expansion(c(0.075,0))) +
  scale_x_continuous(limits = c(min(MobileSensorReadings$Long),
                                max(MobileSensorReadings$Long)),
                     expand = expansion(mult = c(0, 0))) + 
  ggpubr::background_image(img1) +
  # geom_point(data = MobileSensorReadings_byloc, aes(x=Long, y=Lat), alpha = 0.2) +
  geom_point(data = StaticSensorLocations, aes(x = Long, y = Lat), 
                                               shape=23, fill="red", color="black",
                                               size = 4) +
  geom_text(aes(label=StaticSensorLocations$`Sensor-id`, fontface = "bold", size = 12),hjust=-0.75, vjust=1)

```
 

```{r facet and clean}
ggplot(data=StaticSensorReadings, aes(y=Value, x=time)) +
  geom_line() + 
  facet_wrap(~`Sensor-id`) + theme_bw()

StaticSensorReadings$`Sensor-id` <- as.character(StaticSensorReadings$`Sensor-id`)

set.seed(21)
StaticSensorReadings_t <- StaticSensorReadings %>% mutate(hour=lubridate::floor_date(time, "1 hour")) %>%
  group_by(`Sensor-id`, hour) %>% mutate(hourly_Value = sum(Value)) %>%
  full_join(StaticSensorLocations, by = "Sensor-id")
StaticSensorReadings_byloc <- StaticSensorReadings_t %>% sample_frac(0.01)
```

By location

```{r map and static hourly}
fig2 <- StaticSensorReadings_byloc %>%
  plot_ly(
    x = ~Long, y = ~Lat, frame = ~as.character(hour), 
    size = ~hourly_Value, sizes = c(5,20),
    color = ~hourly_Value, 
    type = 'scatter', mode = 'markers', 
    marker = list(
      sizemode = 'diameter',
      colorscale = list(c(0, 'rgba(255, 199, 130,0.75)'),
                        c(1, 'rgba(173, 30, 2, 1)')), showscale=T,
      cauto = F, cmin = 0, cmax =  max(MobileSensorReadings_byloc$hourly_Value),
        # 5172437 for the entire dataset
      line = list(color = 'rgba(51, 6, 0, 1)', width = 2)
      )
    )%>%
  animation_opts(0) %>%
  layout(
    images = list(
      source = raster2uri(as.raster(img1)),
      x = -119.9999, y = 0.008,
      sizex = 0.288152, sizey = 0.230372,
      xref = "x", yref = "y",
      xanchor = "left", yanchor = "bottom",
      sizing = "stretch", opacity = 0.7,
      layer = "below"
    ), xaxis = list(title=""), yaxis = list(title="")
  ) %>%
  animation_slider(
    currentvalue = list(prefix = "timestamp ", font = list(color="red"))
  ) %>% hide_colorbar()

fig2
```


For comparison, max(StaticSensorReadings_t$hourly_Value) = 21,401.26
max(Mobile) = 5,172,437, because more sensors and observation (0.01 sample of the data)
--> sample by number, not fraction. *7705 and 7234*; keep max color in color scale the same

max(MobileSensorReadings_byloc$hourly_Value)/max(StaticSensorReadings_byloc$hourly_Value) = 241.6884